Self Referencing Sequences

### 2014-11-08 draft.tex
new poem

Since $A = \{3,3\}$, $B = \{3,1\}$ and $C = \{1,1\}$, the fraction of 1's in the limiting sequence is $0.5P_{\infty}(B) + P_{\infty}(C)$, and the fraction of 3's in the limiting sequence is $P_{\infty}(A) + 0.5P_{\infty}(B)$. So the density values, if they exist, are
\begin{align*}
&\text{Fraction of 1's: }\texttt{0.397215284799705}\\
&\text{Fraction of 3's: }\texttt{0.602784715200295}.
\end{align*}
We were able to support these calcuations with numerical simulations. We generated the $s((13),3)$ sequence up to 100,000 terms, and we found that the fraction of 1's was approximately $0.398$, and that the fraction of 3's was approximately 0.602.

@@

\section{Haikus}
\emph{Written by Fermi Ma}\\

\noindent One, Two, Two, One, One,\\
Two, One, Two, Two, One, Two, Two,\\
One, One, Two, One, One...\\

\noindent For the final draft,\\
we will improve the haikus\\
(and the whole paper).

\subsection{Poem}

\noindent A sequence refering to its past\\
warrants many questions to be asked.\\
These sequences are deterministic \\
and their read distances an imporant statistic.
\\

\noindent We want to compute the limiting density\\
so we've defined a process.\\
But one would be a fool to not follow our rule.\\
And compute the density for 1, 3.\\

\noindent The big question remains unanswered.\\
The density of 1,2 which seems to be one half.\\
Our rules are for numbers of a certain class.\\
Unfortunetly, dealing with 1,2 is a pain in the a**.\\

>>>>

Since $A = \{3,3\}$, $B = \{3,1\}$ and $C = \{1,1\}$, the fraction of 1's in the limiting sequence is $0.5P_{\infty}(B) + P_{\infty}(C)$, and the fraction of 3's in the limiting sequence is $P_{\infty}(A) + 0.5P_{\infty}(B)$. So the density values, if they exist, are
\begin{align*}
&\text{Fraction of 1's: }\texttt{0.397215284799705}\\
&\text{Fraction of 3's: }\texttt{0.602784715200295}.
\end{align*}
We were able to support these calcuations with numerical simulations. We generated the $s((13),3)$ sequence up to 100,000 terms, and we found that the fraction of 1's was approximately $0.397$, and that the fraction of 3's was approximately 0.603.

@@

\section{Poetry}
\emph{Written by Fermi Ma and Erik Waingarten}\\

\noindent A sequence referring to its past\\
seems quite simple --- not so fast!\\
Sure, it is deterministic,\\
but tell me the density statistic.\\

\noindent Well, try (one, three) and you will see\\
the density* is point six-oh-three.\\
Just write the substitution rule.\\
To miss the answer, you'd be a fool.\\

\noindent Now do the same for one and two,\\
Look at the rule and now you ---\\
Hold on, this doesn't work for numbers of different parity.\\

*if it exists
